Denotational Semantics of Gradual Typing using Synthetic Guarded Domain Theory

### 2024-07-07 paper-new/concrete-relational-model.tex
[paper] slight wording change in section on concrete relational model

\eric{Wording?}
In this section, we build on the ideas used in defining a term model with the
goal of defining a model of the full gradually-typed lambda calculus, i.e., one
that has constructs that model type and term precision.
%
% The purpose of this section is to motivate the need for many of the
% seemingly complicated features of the abstract model introduced in
% Section \ref{sec:abstract-models}.

@@

\subsection{Solution: Splitting into Two Relations}

>>>>

% In the previous section, we gave a denotational semantics to the terms of the
% gradually-typed lambda calculus using the tools of SGDT. We defined a big-step
% semantics for closed terms of type $\nat$, as functions from $\mathbb{N} \to
% ((\mathbb{N} + 1) + 1)$.

\eric{Wording?}
In the previous section, we gave a denotational semantics to the terms of the
gradually-typed lambda calculus using the tools of SGDT. In this section, we
build on the ideas used in defining a term model with the goal of defining a
model of the full gradually-typed lambda calculus, i.e., one that has constructs
that model type and term precision.
%
% The purpose of this section is to motivate the need for many of the
% seemingly complicated features of the abstract model introduced in
% Section \ref{sec:abstract-models}.

@@

\subsection{Solution: Splitting into Two Relations}\label{sec:lock-step-and-weak-bisim}
